---
title: "Summary of Wrangling"
author: "Fadi"
date: "3 January 2018"
output:
  html_document: default
  pdf_document: default
---

### Renaming:
Most columns were aptly named, so there wasn't really much to be adjusted except the "Date Of Stop" and "Time Of Stop" columns; I went ahead and renamed them "Date" & "Time", respectively.

### NA & NONE Values:
Many variables have null values, but not all of them are critical enough to weigh negatively on the analysis. On the Other hand, "Description" had six missing values, which I went ahead and filtered out. 

"Make" also had many NA values, which indicates either that the car was unknown, or a vehicle was not involved in the violation. "Make" also had over 7000 thousand observations that was marked as **NONE**, which is most likely pedestrain violations, I am lead to such conclusion as many of these violations have been registered by "Foot Patrol"

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
library(magrittr)
library(dplyr)
```

```{r include=FALSE}
load(file="Traffic_Violations.RData")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
Traffic_Violations %>% 
  filter(Traffic_Violations$Make == "NONE") %>% 
  select(Description, Make, `Arrest Type`)
```

## NULL Geolocations

There are over 79,000 observations whose "Geolocation" values are **NA**. Many of those coordinates can be arduously extracted from google maps by cross-referencing their corrosponding "Location" values, but this process is tedious at best. I will be putting the resolution of these observations under consideration, for now.

## Other Variables

HAZMAT (Hazardous Material-related) accidents are very rare, and are more or less outliers in this analysis, so I have excluded these observations for the time being.

Article, Agency, SubAgency have inconsequential details, so I went ahead and disposed of these columns.